Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-08-31 ms.tex
updating OTIS grism test results with dramatic improvements after row-by-row and column-by-column subtraction.

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{tser_LW_OTIS.pdf}{0.6\textwidth}{Grism Time Series}}
\caption{Time series of the simultaneous SW/LW Time Series Stability test
\textcolor{red}{Thing to try: did I try a circular aperture centered on the knot? try to use centroid from SW to adjust the position of the source extraction box}
}\label{fig:otisLWSWtser}
\end{figure*}

@@

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{raw_tser_LWgrisMPPVertBackbox_otisSWLWsimult.pdf}{0.49\textwidth}{Slope Images}
\fig{raw_tser_LWgrisMMMRowColSubVertBackbox_otisSWLWsimult.pdf}{0.49\textwidth}{Column-by-column and row-by-row subtraction}}
\caption{The grism time series contains subtraction correlated read noise due to pre-amplifier offsets in the vertical direction and 1/f noise in the horizontal direction.
Row-by-row-subtraction dramatically decreases the noise due to 1/f noise.
}\label{fig:otisLWSWtserShift}
\end{figure*}

>>>>

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{tser_LWSW_OTIS.pdf}{0.6\textwidth}{Grism Time Series}}
\caption{Time series of the simultaneous SW/LW Time Series Stability test
\textcolor{red}{Thing to try: did I try a circular aperture centered on the knot? try to use centroid from SW to adjust the position of the source extraction box}
}\label{fig:otisLWSWtser}
\end{figure*}

@@

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{raw_tser_LWgrisMPPVertBackbox_otisSWLWsimult.pdf}{0.49\textwidth}{Slope Images}
\fig{raw_tser_LWgrisMMMRowColSubVertBackbox_otisSWLWsimult.pdf}{0.49\textwidth}{Column-by-column and row-by-row subtraction}}
\caption{The grism time series contains correlated read noise due to pre-amplifier offsets over each amplifier and 1/f noise in the horizontal (fast read) direction.
Row-by-row-subtraction dramatically decreases the noise due to 1/f noise while column-by-column subtraction dramatically decreases the pre-amplifier offset noise.
}\label{fig:otisLWSWtserShift}
\end{figure*}
